Fast Sorting on Modern Computers

### 2005-08-14 docs/tech_report/method.tex
done spell check. some errors found
added bit about mispredictions vs misses, and about the scale of software prediction graphs

\subsection{Software Predictor}
The software predictor used was a series of macros and functions which
maintained the state of a bimodal branch predictor at a particular point in the
program. Statistics about each branch were collected, and dumped into text
files, from which scripts created graphs to display them. Some sample code is
shown in Figure \ref{Sample code using the software predictor}.

@@

These simulations were run a on Pentium 4 1.6GHz, which had an 8-way, 256K level
2 cache, with a 64-byte cache line. The level 1 caches are 8K 4-way associative
caches, with seperate instruction and data level 1 caches.

>>>>

\subsection{Software Predictor}
The software predictor used was a series of macros and functions which
maintained the state of a bimodal branch predictor at a particular point in the
program. Statistics about each branch were collected, and dumped into text
files, from which scripts created graphs to display them. Some sample code is
shown in Figure \ref{Sample code using the software predictor}. Each of the
graphs produced by the predictors uses the same scale; this way, it is possible
to visually compare the results from one sort to another.

@@

These simulations were run a on Pentium 4 1.6GHz, which had an 8-way, 256K level
2 cache, with a 64-byte cache line. The level 1 caches are 8K 4-way associative
caches, with separate instruction and data level 1 caches.
